Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-12 manuscript.tex
add matlab fig to tikz fig converter
mat2pdf moved to template

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig10.eps
        src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\tau$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights $\hat\theta_i$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

@@

>>>>

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
      \includegraphics
    %   \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        fig/Fig1.pdf
        % src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\tau$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights $\hat\theta_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

@@

% ------------------------------------
% Karsh-Kuhn-Tucker (KKT) conditions}
% ------------------------------------
\subsubsection{Satisfaction of Karsh-Kuhn-Tucker (KKT) conditions}

\color{red}
The KKT conditions defined in \cite[Def. @@]{Nocedal:2006aa} were satisfied in the simulation, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
\color{black}
